%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
% \documentclass[print]{friggeri-cv}

\begin{document}
\header{charles}{moraes}
       {computer science}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    \href{mailto:raverblazer@gmail.com}{raverblazer@gmail.com}
    \href{http://www.linkedin.com/in/charlesdm}{\faLinkedinSign \space  /in/charlesdm}
    \href{https://github.com/streeck}{\faGithubSign \space github.com/streeck}
    ~
    (11) 5066-7442
    (11) 99421-0220
    ~
    Avenida Moaci 1885
    Planalto Paulista
    04083-005
    São Paulo, SP
    Brazil
  \section{languages}
    native portuguese
    fluent english
    spanish notions
  \section{programming}
    Python, R
    Django, Numpy, Scipy
    Ruby on Rails
    C, C++, Java
    PostgreSQL
    JavaScript
    CSS3 \& HTML5
\end{aside}

\section{interests}

web/mobile development, artificial intelligence, machine learning, natural language processing, recommendation, data mining, innovation, new technologies

\section{education}

\begin{entrylist}
  %\entry
  %  {since 2011}
  %  {Ph.D. {\normalfont candidate in Computer Science}}
  %  {Federal University of São Carlos, Sorocaba}
  %  {\emph{A Quantified Theory of Social Cohesion.}}
  \entry
    {since 2015}
    {M.Sc.}
    {Federal University of São Carlos -- UFSCar, Sorocaba}
    {Majoring in Computer Science,\\
    Specialization in Machine Learning}
  \entry
    {2011 – 2014}
    {B.Sc.}
    {Federal University of São Carlos -- UFSCar, Sorocaba}
    {Majoring in Computer Science}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2013 – 2014}
    {São Paulo Research Foundation – FAPESP}
    {Research Internship.}
    {\emph{Towards Automatically Detection of Blog Comment Spamming.}}
  \entry
    {2009 – 2011}
    {Creche Especial Maria Claro}
    {Volunteer job.}
    {\emph{Assistance in the treatment of children with multiple disabilities.}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {since 2014}
    {TubeSpam \emph{(in development)}}
    {\href{http://lasid.sor.ufscar.br/tubespam}{lasid.sor.ufscar.br/tubespam}}
    {Explore the presence of \emph{spam} in the YouTube comments section. Apply Machine Learning techniques, such as SVM, Na\"ive Bayes and semi-supervised learning, to automatically distinguish \emph{spam} and legitimate comments.}
  \entry
    {2013}
    {Animal-zoo \emph{(in Portuguese)}}
    {\href{http://animal-zoo.herokuapp.com}{animal-zoo.herokuapp.com}}
    {Help zoos taking care of wild animals. Is currently maintained by other students of the Federal University of São Carlos -- UFSCar, Sorocaba.}
\end{entrylist}

\end{document}
